### 2015-12-02 paper.tex
Move comment to issue #26

The behavior of the power coefficient at $\lambda=3.1$ is plotted in
Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
highlighted. We see that the power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$ \textbf{\textit{[define Rec]}},
beyond which there appears to be a small, linear, positive trend. The tendency
of $C_P$ to continue increasing slightly could be an effect of lower virtual
camber \textbf{\textit{[I think we need to elaborate more on this. On its own, this sentence sounds very speculative]}} when compared to the strong $Re$-independence of the higher $c/R$
UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.

>>>>

The behavior of the power coefficient at $\lambda=3.1$ is plotted in
Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
highlighted. We see that the power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$
\textbf{\textit{[define Rec]}}, beyond which there appears to be a small,
linear, positive trend. The tendency of $C_P$ to continue increasing slightly
could be an effect of lower virtual camber when compared to the strong
$Re$-independence of the higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
